### 2018-10-24 Chapters/Chapter3.tex
asdf

Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar. Now we can follow the same procedure as in the previous section to obtain \ref{2ndOH}

\begin{equation}
\hat{H}'^{(2)}(t) = \frac{1}{2}\sum_{mn} \left( \frac{\left[\hat{T}_{1n}, \hat{T}_{-1(m-n)} \right]}{\text{U}+n\omega} - \frac{\left[\hat{T}_{-1n}, \hat{T}_{1(m-n)} \right]}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

As before, we are only interested on how the Hamiltonian acts on the subspace of doublon number $d=0$. In that subspace we have:

\begin{equation}
\hat{H}_{eff}(t) = \hat{P}_0 \hat{H}'^{(2)}(t)\hat{P}_0 = - \frac{1}{2}\sum_{mn} \left( \frac{\hat{T}_{-1(m-n)}\hat{T}_{1n}  }{\text{U}+n\omega} + \frac{\hat{T}_{-1n}\hat{T}_{1(m-n)}}{\text{U}-n\omega} \right) e^{im\omega t}
\end{equation}

Where,

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ij,a}^{\sigma_1\sigma_2}\Gamma_{ji,b}^{\sigma_3\sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4}
\end{equation}

For any integers $a,b$. Therefore:

\begin{equation}
\hat{H}_{eff}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \left\{ \frac{\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4}}{\text{U}+n\omega} + \frac{\Gamma_{ij,n}^{\sigma_1\sigma_2}\Gamma_{ji,(m-n)}^{\sigma_3\sigma_4}}{\text{U}-n\omega} \right\} e^{im\omega t}
\end{equation}

We can rewrite:

\begin{align*}
\Gamma_{ij,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ji,n}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_n(\alpha_{ji})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})m}\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
\end{align*}

@@

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}

@@

\begin{align*}
\hat{H}_{eff}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
&= \hat{H}_J'(t)+\hat{H}_D'(t)
\end{align*}

@@

\begin{equation}
\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{m-n}(\alpha_{ij})\mathcal{J}_{-n}(\alpha_{ij})}{\text{U}+n\omega} +
    \frac{\mathcal{J}_n(\alpha_{ij})\mathcal{J}_{n-m}(\alpha_{ij})}{\text{U}-n\omega}    
    \right\}e^{im\omega t}
\end{equation}

>>>>

Where we define $\Gamma_{ij,m}^{\sigma\sigma'} = e^{i(\frac{\pi}{2}-\theta_{ij})m} \mathcal{J}_m(\alpha_{ij})(\delta_{\sigma, \sigma'}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma \sigma'})$ a scalar. Now we can follow the same procedure as in the previous section that lead to \ref{HeffSimplified}:

\begin{equation}
\hat{H}_{\text{eff}}(t) = \hat{P}_0 \hat{H}'^{(2)}(t) \hat{P}_0 = -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0 \left(\hat{T}_{-1(m-n)}\hat{T}_{1n} + \hat{T}_{-1-n}\hat{T}_{1(m+n)} \right) \hat{P}_0 }{\text{U}+n\omega} \right\} e^{im\omega t}
\end{equation}

The product of hopping operators restricted on this subspace can be written as:

\begin{equation}
\hat{P}_0 \hat{T}_{-1a}\hat{T}_{1b} \hat{P}_0 = \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4}
\end{equation}

For any integers $a,b$ labeling any Fourier modes. Therefore:

\begin{equation}
\hat{H}_{\text{eff}}(t) = -\frac{1}{2}\sum_{mn} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \hat{c}_{j\sigma_1}^\dagger\hat{c}_{i\sigma_2}\hat{c}_{i\sigma_3}^\dagger\hat{c}_{j\sigma_4} \left\{ \frac{\Gamma_{ji,(m-n)}^{\sigma_1\sigma_2}\Gamma_{ij,n}^{\sigma_3\sigma_4} + \Gamma_{ji,-n}^{\sigma_1\sigma_2}\Gamma_{ij,(m+n)}^{\sigma_3\sigma_4} }{\text{U}+n\omega}  \right\} e^{im\omega t}
\end{equation}

We can write:

\begin{align*}
\Gamma_{ji,a}^{\sigma_1\sigma_2}\Gamma_{ij,b}^{\sigma_3\sigma_4} &= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{a}(\alpha_{ji})\mathcal{J}_b(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0+\bs{\Delta}_{ji}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij})(\delta_{\sigma_1, \sigma_2}t_0-\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_1 \sigma_2})(\delta_{\sigma_3, \sigma_4}t_0+\bs{\Delta}_{ij}\bs{\sigma}_{\sigma_3 \sigma_4}) = \\
&= e^{i(\frac{\pi}{2}-\theta_{ij})(a+b)}\mathcal{J}_{-a}(\alpha_{ij})\mathcal{J}_{b}(\alpha_{ij}) \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) + \mathcal{O}(\bs{\Delta}_{ij}^2) \right]
\end{align*}

@@

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
\end{equation}

@@

\begin{align*}
\hat{H}_{\text{eff}}(t) &\approx -\frac{1}{2}\sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\times \left[ \delta_{\sigma_1, \sigma_2}\delta_{\sigma_3, \sigma_4}t_0^2+t_0\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4}) \right]\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= -\frac{t_0^2}{2} \sum_{\langle i,j \rangle \sigma, \sigma'} \left(\frac{1}{2}\delta_{\sigma \sigma'} + \bs{S}_i\bs{\sigma}_{\sigma' \sigma}\right)\left(\frac{1}{2}\delta_{\sigma \sigma'}-\bs{S}_j\bs{\sigma}_{\sigma \sigma'}\right)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) - \\
&- \frac{t_0}{2} \sum_{\langle i,j \rangle \sigma_1, \sigma_2, \sigma_3, \sigma_4} \left(\frac{1}{2}\delta_{\sigma_1 \sigma_4} + \bs{S}_i\bs{\sigma}_{\sigma_4 \sigma_1}\right)\left(\frac{1}{2}\delta_{\sigma_2 \sigma_3}-\bs{S}_j\bs{\sigma}_{\sigma_2 \sigma_3}\right) \times \\
&\bs{\Delta}_{ij}(\delta_{\sigma_3,\sigma_4}\bs{\sigma}_{\sigma_1 \sigma_2}-\delta_{\sigma_1,\sigma_2}\bs{\sigma}_{\sigma_3 \sigma_4})\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) = \\
&= \sum_{\langle i,j \rangle} \left( t_0^2 \bs{S}_i\bs{S}_j + 2it_0\bs{\Delta}_{ij} \bs{S}_i \times \bs{S}_j \right) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) =\\
&= \sum_{\langle i,j \rangle} J_{ij}(t)\bs{S}_i\bs{S}_j +\bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j = \\
&= \hat{H}_J'(t)+\hat{H}_D'(t)
\end{align*}

@@

\begin{equation}
\bs{D}_{ij} = 2it_0 \bs{\Delta}_{ij} \sum_{mn}e^{i(\frac{\pi}{2}-\theta_{ij})m} \left\{ 
    \frac{\mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij}) + \mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{m+n}(\alpha_{ij})}{\text{U}+n\omega} \right\}e^{im\omega t}
\end{equation}

### 2018-10-24 Chapters/SGraphene.tex
asdf

In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. However, if inversion symmetry is broken, a Rashba spin orbit interaction term is allowed between nearest neighbors. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:

@@

\begin{align*}
\hat{H}_{\text{eff}}(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}^1(t) + \hat{H}_{\text{eff}}^2(t)
\end{align*}

For $\hat{H}_{\text{eff}}^1(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}. For $\hat{H}_{\text{eff}}^2(t)$ the interaction will be between next-nearest neighbors:

\begin{align*}
\hat{H}_{\text{eff}}^2(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \sum_{\langle \langle i,j \rangle \rangle \sigma_1 \sigma_2 \sigma_3 \sigma_4} \left\{ \frac{\hat{P}_0 (\Pi_{ji,(m-n)}^{\sigma_1\sigma_2}\Pi_{ij,n}^{\sigma_3\sigma_4} + \Pi_{ji,(-n)}^{\sigma_1\sigma_2}\Pi_{ij,(m+n)}^{\sigma_3\sigma_4}) \hat{P}_0}{U+n\omega} \right\}\hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} e^{im\omega t} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \sum_{mn} \frac{e^{i(\frac{\pi}{2}-\theta_{ij})m}}{\text{U}+n\omega} \left\{ \mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij}) \right\} e^{im \omega t} \\
& \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\}
\end{align*}

@@

\begin{equation}
\hat{H}_{\text{eff}}^2(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
\end{equation}

@@

>>>>

In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. However, if inversion symmetry is broken by i.e. an external electric field in the $\hat{z}$ direction, a Rashba spin orbit interaction term is allowed between nearest neighbors. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:

@@

\begin{align*}
\hat{H}_{\text{eff}}(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^1\hat{T}_{1n}^1 + \hat{T}_{-1-n}^1\hat{T}_{1(m+n)}^1)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&-\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} = \hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t)
\end{align*}

For $\hat{H}_{\text{eff}}'(t)$ the derivation is identical to that in the previous section with $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ so $\hat{H}_{\text{eff}}^1(t) = \sum_{\langle i,j \rangle} (J_{ij}(t) \bs{S}_i\bs{S}_j + \bs{D}_{ij}(t)\bs{S}_i \times \bs{S}_j)$ with the same exchange and DMI interaction as in \ref{JijHSOI} and \ref{DijHSOI}. For $\hat{H}_{\text{eff}}''(t)$ the interaction will be between next-nearest neighbors:

\begin{align*}
\hat{H}_{\text{eff}}''(t) &= -\frac{1}{2}\sum_{mn} \left\{ \frac{\hat{P}_0  (\hat{T}_{-1(m-n)}^2\hat{T}_{1n}^2 + \hat{T}_{-1-n}^2\hat{T}_{1(m+n)}^2)\hat{P}_0}{U+n\omega} \right\} e^{im\omega t} \\
&= -\frac{1}{2}\sum_{mn} \sum_{\langle \langle i,j \rangle \rangle \sigma_1 \sigma_2 \sigma_3 \sigma_4} \left\{ \frac{\hat{P}_0 (\Pi_{ji,(m-n)}^{\sigma_1\sigma_2}\Pi_{ij,n}^{\sigma_3\sigma_4} + \Pi_{ji,(-n)}^{\sigma_1\sigma_2}\Pi_{ij,(m+n)}^{\sigma_3\sigma_4}) \hat{P}_0}{U+n\omega} \right\}\hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} e^{im\omega t} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \sum_{mn} \frac{e^{i(\frac{\pi}{2}-\theta_{ij})m}}{\text{U}+n\omega} \left\{ \mathcal{J}_{n-m}(\alpha_{ij})\mathcal{J}_{n}(\alpha_{ij})+\mathcal{J}_{n}(\alpha_{ij})\mathcal{J}_{n+m}(\alpha_{ij}) \right\} e^{im \omega t} \\
& \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\} \\
&= -\frac{\Delta^2}{2} \sum_{\langle \langle i,j \rangle \rangle} \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left\{ \sum_{\sigma_1 \sigma_2 \sigma_3 \sigma_4} \sigma_{\sigma_1 \sigma_2}^z\sigma_{\sigma_3 \sigma_4}^z \hat{c}_{i\sigma_1}^\dagger\hat{c}_{j\sigma_2}\hat{c}_{j\sigma_3}^\dagger\hat{c}_{i\sigma_4} \right\}
\end{align*}

@@

\begin{equation}
\hat{H}_{\text{eff}}''(t) = \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
\end{equation}

@@

This describes a type of anisotropic exchange interaction. Notice that the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}.

Together with exchange and DMI interaction obtained in the previous section the total effective Hamiltonian in this system is:

\begin{align}
\hat{H}_{\text{eff}}(t) = &\hat{H}_{\text{eff}}'(t) + \hat{H}_{\text{eff}}''(t) = \sum_{\langle i,j \rangle} \left( J_{ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{ij}(t) \bs{S}_i \times \bs{S}_j \right) \nonumber \\
&+ \sum_{\langle \langle i,j \rangle \rangle} H_{ij}(t) (S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y)
\end{align}

Where $J_{ij}(t)$ and $\bs{D}_{ij}(t)$ have been obtained in \ref{JijHSOI} and \ref{DijHSOI} and we take $\Delta_{ij} = i\Delta_R (R_{ij}^y, - R_{ij}^x, 0)$ to obtain:

\begin{align*}
J_{ij}(t) &= t_0^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{ij}(t) &= -2t_0\Delta_R (R_{ij}^y, - R_{ij}^x, 0) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}

Where $J_{ij}(t)$ and $\bs{D}_{ij}(t)$ have been defined in \ref{JijHSOI} and \ref{DijHSOI}.
